---
title: "AE 03"
subtitle: "Visualizing Star Wars characters"
date: "Due: August 26, 11:59PM"
author: "YOUR NAME GOES HERE"
output: 
  html_document: 
    toc: TRUE
    toc_float: TRUE
    fig_height: 4
    fig_width: 9
---

```{r load-packages, include=FALSE}
library(tidyverse)
```

### Recap: individual assignment workflow

- Click on the link provided in the slides to create your own private repo for 
this exercise.

- Go to the `ae-03-star-wars-your-name-here` repo on GitHub that you created

- Click on the green **Code** button, **Use HTTPS**, and click on the clipboard 
icon to copy the repo URL.

- Go to RStudio and go to *File* $\rightarrow$ *New Project* $\rightarrow$ 
*Version Control* $\rightarrow$ *Git, then paste the URL or your assignment
repo into the dialog box *Repository URL*.

- Browse to an appropriate place (perhaps creating a new folder if desired) on
the virtual machine for a folder to be created that contains the AE materials.

- Click *Create Project*, and log in using your GitHub credentials. If you have
successfully logged in, the files from your repo will be displayed in the 
*Files* pane.

- Configure git by typing the following in the Console (using your GitHub
username and e-mail as appropriate)

```{r eval=FALSE}
library(usethis)
use_git_config(user.name="your name", user.email="your email")
```

**RStudio and GitHub can now commmunicate with each other and you are ready to do the exercise!**

## Practice with ggplot

1. Modify the following plot to change the color of all points to `"pink"`. Knit the document.

```{r starwars-plot}
ggplot(data = starwars, 
       mapping = aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "darkblue") +
  labs(title = "_____" , size = "_____", x = "_____", y = "_____")
```

2. Add labels for title, x and y axes, and size of points. Knit again.

3. Suppress the warning message in your R chunk by adding an appropriate option.
Be careful about commas!

4. Create a scatterplot visualization of your choice. What relationship(s) 
do(es) your plot illustrate?

5. Try to make a histogram of a numerical variable of your choice by modifying 
the `geom_[something]` function (I know we haven't covered it formally - where
might you go for help?).

## Stage, commit and push

1. Commit the changes you made using an simple and informative message. You can 
find the Commit box in the Git tab in the top right pane. Remember, 
**these changes must first be staged**.
2. **Push** your changes to your repo on GitHub. You will have to log in again.
3. Check your repo on GitHub and see the updated files.